TBD

### 2016-10-04 paper.tex
implemented workaround for mathtools

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{subfigure}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{graphicx}
\usepackage{mathtools}

@@

\newcommand\coolover[2]{\mathrlap{\smash{\overbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}^{\mbox{$#1$}}}}#2}

\newcommand\coolunder[2]{\mathrlap{\smash{\underbrace{\phantom{%
    \begin{matrix} #2 \end{matrix}}}_{\mbox{$#1$}}}}#2}

\newcommand\coolleftbrace[2]{%
#1\left\{\vphantom{\begin{matrix} #2 \end{matrix}}\right.}

\newcommand\coolrightbrace[2]{%
\left.\vphantom{\begin{matrix} #1 \end{matrix}}\right\}#2}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g}_{q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{eqnarray}
 \bd &=& [d_{pq}] \big \} ~ [pq] = 1\cdots B ~ (p<q),\nonumber\\
 \bv &=& [g_p y_{\phi_{pq}} \conj{g}_q]  \big \} ~ [pq] = 1\cdots B ~ (p<q),\nonumber\\
 \bn &=& [n_{pq}]  \big \} ~ [pq] = 1\cdots B ~ (p<q).\label{eq:vec_definitions}
\end{eqnarray}
In Eq.~\eqref{eq:vec_definitions}, $B$ denotes the number of baselines in the array.

@@

\subsection{LOGCAL}
One of the best known algorithms that is currently used to perform redundant calibration involves the use of logarithms. If we ignore the noise term then we can 
rewrite Eq.~\eqref{eq:vis_red} as
\begin{eqnarray}
\ln |d_{ij}| &=& \ln |g_i| + \ln |g_j| + \ln |y_{\phi_{ij}}| \label{eq:logcal_amp}\\
\angle d_{ij} &=& \angle g_i - \angle g_j + \angle \phi_{ij} \label{eq:logcal_phase}
\end{eqnarray}

We can easily express Eq.~\eqref{eq:logcal_amp} with the following linear system
\begin{equation}
\widetilde{\bd} = \bA\bz, 
\end{equation}
which has the following least-squares solution
\begin{equation}
\bz = (\bA^T\bA)^{-1}\bA^T\widetilde{\bd},
\end{equation}
where
\begin{equation}
\widetilde{\bd} = [\ln |d_{pq}|] \big \} ~ [pq] = 1,\cdots,B ~ (p<q),\nonumber\\ 
\end{equation}
and
\begin{equation}
\bA = 
\begin{bmatrix}
\coolover{{\scriptstyle j=1,\ldots,N}}{\delta^j_p\vee\delta^j_q} & \coolover{{\scriptstyle k=1,\ldots,L}\!\!\!\!}{~\delta_{\phi_{pq}}^k}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\delta_{\phi_{pq}}^k}{[pq] = 1,\ldots,B~(p<q)}
\end{matrix}.
\end{equation}

Moreover, $(*)^T$ denotes the transpose of its operand, $(*)^{-1}$ denotes matrix inversion, $\vee$ denotes the logical or operator and
\begin{equation}
\delta_y^x  = \begin{cases}
          1 & \textrm{if}~x=y\\
          0 & \textrm{otherwise}
         \end{cases}.
\end{equation}
A similar linear system can be constructed for Eq.~\eqref{eq:logcal_phase}.

\subsection{LINCAL}
Assume that $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$ are real valued variables.
Substituting $g_i$ with $e^{\eta_i - i \varphi_i}$, $g_j$ with $e^{\eta_j - i \varphi_j}$ and $y_{\phi_{ij}}$ with $e^{\eta_{\widetilde{\phi}_{ij}}- i \widetilde{\varphi}_{\phi_{ij}}}$ in Eq.~\eqref{eq:vis_red} results in  
\begin{equation}
\label{eq:lincal}
d_{ij} =  e^{\eta_i - i \varphi_i} e^{\widetilde{\eta}_{\phi_{ij}}- i \widetilde{\varphi}_{\phi_{ij}}} e^{\eta_j + i \varphi_j} + n_{ij}.
\end{equation}

A possible approach one can use to solve the unknowns in Eq.~\eqref{eq:lincal} is to write down the Taylor expansion of the first term of the right hand side of Eq.~\eqref{eq:lincal} around some 
initial fiducial guess of $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$, which we denote with 
$\eta_i^0,\eta_j^0,\widetilde{\eta}_{\phi_{ij}}^0,\varphi_i^0,\varphi_j^0$ and $\widetilde{\varphi}_{\phi_{ij}}^0$, and then to solve the perturbations from this 
initial guess that minimize the difference between the right and left hand side of Eq.~\eqref{eq:lincal}. Once the perturbation values 
have been computed it is trivial to obtain an estimate of $g_i$, $g_j$ and $y_{\phi_{ij}}$.

If we Taylor expand the first term on the right hand side of Eq.~\eqref{eq:lincal} around a fiducial initial guess we obtain
\begin{equation}
\label{eq:taylor_expansion}
d_{ij} = v_{ij}^0[1+\Delta \eta_i + \Delta \eta_j + i \varphi_i - i \Delta \varphi_j + \Delta \widetilde{\eta}_{\phi_{ij}} + i\Delta \widetilde{\eta}_{\phi_{ij}}] + n_{ij}, 
\end{equation}
where
\begin{equation}
v_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\widetilde{\eta}_{\phi_{ij}}^0 - i \widetilde{\varphi}_{\phi_{ij}}^0} e^{\eta_j^0 + i \varphi_j^0}, 
\end{equation}
and $\eta_i^0,\eta_j^0,\widetilde{\eta}_{\phi_{ij}}^0,\varphi_i^0,\varphi_j^0$ and $\widetilde{\varphi}_{\phi_{ij}}^0$ respectively denote the initial guess for $\eta_i,\eta_j,\widetilde{\eta}_{\phi_{ij}},\varphi_i,\varphi_j$ and $\widetilde{\varphi}_{\phi_{ij}}$.
Eq.~\eqref{eq:taylor_expansion} can be used to construct the following linear system
\begin{equation}
\breve{\br} = \bJ\Delta\widetilde{\bz}, 
\end{equation}
where 
\begin{equation}
\breve{\br} = [d_{ij}-v_{ij}^0] \big \} ~ [ij] = 1\cdots 2B, 
\end{equation}
\begin{equation}
\label{eq:jac_lincal}
\bJ = \begin{bmatrix}
      \bN & \bM\\
      \conj{\bN} & \conj{\bM}
      \end{bmatrix}
\end{equation}
and
\begin{equation}
\Delta\widetilde{\bz} = 
\begin{bmatrix}
\Delta \eta_i \\
\Delta \varphi_j \\
\Delta \widetilde{\eta}_k \\
\Delta \widetilde{\varphi}_l \\
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\eta_i}{i = 1\cdots N}\\
\coolrightbrace{\eta_i}{j = 1\cdots N}\\
\coolrightbrace{\eta_i}{k = 1\cdots L}\\
\coolrightbrace{\eta_i}{l = 1 \cdots L}
\end{matrix}.
\end{equation}

In Eq.~\eqref{eq:jac_lincal}

\begin{eqnarray}
\bN &=& 
\begin{bmatrix}
\coolover{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{\frac{\partial v_{pq}}{\partial \eta_j}} & \coolover{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{~\frac{\partial v_{pq}}{\partial \varphi_k}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
&=& \begin{bmatrix}
\coolunder{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{n_{j,pq}} & \coolunder{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{(-1)^{\delta_q^k}i n_{k,pq}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
\end{eqnarray}

\begin{eqnarray}
\bM &=& 
\begin{bmatrix}
\coolover{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,L}}{\frac{\partial v_{pq}}{\partial \widetilde{\eta}_j}} & \coolover{\!\!\!\!{\scriptstyle k=1,\ldots,L}}{~\frac{\partial v_{pq}}{\partial \widetilde{\varphi}_k}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
&=& \begin{bmatrix}
\coolunder{\!\!\!\!\!\!\!{\scriptstyle j=1,\ldots,N}}{m_{j,pq}} & \coolunder{\!\!\!\!{\scriptstyle k=1,\ldots,N}}{i m_{k,pq}}
\end{bmatrix}
\begin{matrix}% matrix for right braces 
\coolrightbrace{\frac{\partial v_{ij}}{\partial \eta_j}}{\scriptstyle [pq] = 1,\ldots,B~(p<q)}
\end{matrix}\\
\end{eqnarray}

Moreover,
\begin{equation}
n_{j,pq} = (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq} 
\end{equation}
and
\begin{equation}
m_{j,pq} = \delta_{\phi_{pq}}^{j} v_{pq}.
\end{equation}

@@

% fiducial initial guess 
% 
% The following partial derivatives are now easily computed
% 
% \begin{eqnarray}
% \frac{c_{ij}}{\partial \eta_i} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
% \frac{c_{ij}}{\partial \varphi_i} &=&  -i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
% \frac{c_{ij}}{\partial \eta_j} &=& y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\ 
% \frac{c_{ij}}{\partial \varphi_j} &=&  i y_{i-j} e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}\\
% \frac{y_{i-j}}{\partial \varphi_j} &=&  e^{\eta_i - i \varphi_i} e^{\eta_j - i \varphi_j}
% \end{eqnarray}
% 
% 
% The Wirtinger derivative is used in the last equation.
% 
% \begin{eqnarray}
% c_{ij} &\approx& c_{ij}^0 + \Delta \eta_i(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) + \Delta \eta_j(y_{i-j}^0 e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% && -i\Delta\varphi_i (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}) +i\Delta\varphi_j (y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% && y_{i-j}^1(y_{i-j}^0e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0})\\
% &\approx&  c_{ij}^0 + e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i))
% \end{eqnarray}
% 
% \begin{equation}
% \label{eq:residual}
% r_{ij} = \delta_{ij} = c_{ij}-c_{ij}^0 = e^{\eta_i^0 - i \varphi_i^0} e^{\eta_j^0 - i \varphi_j^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_i+ \Delta \eta_j - i\Delta\varphi_i + i\Delta\varphi_i)) 
% \end{equation}
% 
% Eq.~\ref{eq:residual} allows us to construct the following linear system:
% 
% \begin{equation}
% \boldsymbol{J}[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = \boldsymbol{r}, 
% \end{equation}
% 
% where $\boldsymbol{J}$ is equal to 
% \begin{equation}
% \boldsymbol{J} = \bigg [\overbrace{\frac{c_{pq}}{\partial \eta_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial \varphi_i}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial y_{t}}}^{t=1\cdots r_s} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q) 
% \end{equation}
% or
% \begin{equation}
% \boldsymbol{J} = \bigg [\frac{c_{pq}}{\partial \boldsymbol{\eta}},~\frac{c_{pq}}{\partial \boldsymbol{\varphi}},~\frac{c_{pq}}{\partial \boldsymbol{y}} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q). 
% \end{equation}
% 
% The last column is again a Wirtinger derivative.
% 
% Which means we can obtain the least-squares estimate as follows:
% 
% \begin{equation}
% [\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = [\boldsymbol{J}^H\boldsymbol{J}]^{-1}\boldsymbol{J}^H\boldsymbol{r}.
% \end{equation}

>>>>

%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%
\usepackage{subfigure}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{graphicx}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Signal-to-noise Ratio}
If the array is redundant and the function $\phi_{ij}$ is known we can rewrite Eq.~\eqref{eq:vis_definition} as
\begin{equation}
\label{eq:vis_red}
d_{pq} = g_{p}\conj{g}_{q}y_{\phi_{pq}} + n_{pq}.
\end{equation}
Eq.~\eqref{eq:vis_red} can also be expressed in the following vector form 
\begin{equation}
\bd = \bv + \bn, 
\end{equation}
where 
\begin{align}
 \left [ \bd \right]_{\alpha_{pq}} &= d_{pq}, & \left [ \bv \right ]_{\alpha_{pq}} &= g_p y_{\phi_{pq}} \conj{g}_q\nonumber\\
 \left [ \bn \right ]_{\alpha_{pq}} &= n_{pq}. &  &\label{eq:vec_definitions}
\end{align}
In Eq.~\eqref{eq:vec_definitions}, the size of the three vectors are equal to $B$ (i.e. $p<q$), which denotes the number of baselines in the array. Moreover,
\begin{equation}
\alpha_{pq} =
\begin{cases}
(q-p) + (p-1)\left (N-\frac{1}{2}p \right ) & \textrm{if}~p<q\\
B + (p-q) + (q-1)\left (N-\frac{1}{2}q \right )) & \textrm{if}~p>q\\
%B+q + \frac{1}{2}(p-1)(p-2) & \textrm{if}~p>q\\
0 & \textrm{otherwise}
\end{cases}.
\end{equation}
The easiest way to construct the vectors in Eq.~\ref{eq:vec_definitions} is to enumerate through the composite indexes $pq$ in the following order $12, 13,\cdots,1N,23,\cdots$.
For each composite index we then compute the right hand side of the appropriate vector element definition which we then need to assign to the 
correct vector position. The correct position is calculated with $\alpha_{pq}$. Using the aforementioned order, however, allows you to fill the vector in numerical order, i.e. $12,13,\cdots,1N,23,\cdots \xrightarrow{\alpha_{pq}} 1,2,3,\cdots,B$.

@@

\subsection{LOGCAL}
NEED BETTER INTRO\\
One of the best known algorithms that is currently used to perform redundant calibration involves the use of logarithms. If we ignore the noise term then we can 
rewrite Eq.~\eqref{eq:vis_red} as
\begin{eqnarray}
\ln |d_{pq}| &=& \ln |g_p| + \ln |g_q| + \ln |y_{\phi_{pq}}| \label{eq:logcal_amp}\\
\angle d_{pq} &=& \angle g_p - \angle g_q + \angle \phi_{pq} \label{eq:logcal_phase}
\end{eqnarray}

We can easily express Eq.~\eqref{eq:logcal_amp} with the following linear system
\begin{equation}
\widetilde{\bd} = \bA\widetilde{\bz}, 
\end{equation}
where
\begin{equation}
\left [ \widetilde{\bd}\right ]_{\alpha_{pq}} = \ln |d_{pq}|,\nonumber\\ 
\end{equation}
\begin{equation}
\widetilde{\bz} = \begin{bmatrix}
                  \ln | \bg |\\
                  \ln | \by |
                  \end{bmatrix},
\end{equation}
with $\bg = [g_1,g_2,\cdots,g_N]^T$ and $\by = [y_1,y_2,\cdots,y_L]^T$.

Furthermore,
\begin{equation}
\label{eq:A}
\bA = \begin{bmatrix}
       \bA_1 & \bA_2
      \end{bmatrix}
\end{equation}
and
\begin{equation}
\left [ \bA_1 \right ]_{\alpha_{pq},j} = \delta^j_p\vee\delta^j_q,  ~~~ \left [ \bA_2 \right ]_{\alpha_{pq},j} = \delta_{\phi_{pq}}^j. 
\end{equation}

The dimensions of $\bA_1$ and $\bA_2$ are $B\times N$ and $B\times L$.
Moreover, $\vee$ denotes the logical or operator and
\begin{equation}
\delta_y^x  = \begin{cases}
          1 & \textrm{if}~x=y\\
          0 & \textrm{otherwise}
         \end{cases}.
\end{equation}
A similar linear system can be constructed for Eq.~\eqref{eq:logcal_phase}.\\

NEED TO ROUND OF HERE STILL

\subsection{LINCAL}
Assume that $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$ are real valued variables.
Substituting $g_p$ with $e^{\eta_p - i \varphi_p}$, $g_q$ with $e^{\eta_q - i \varphi_q}$ and $y_{\phi_{pq}}$ with $e^{\eta_{\widetilde{\phi}_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}}$ in Eq.~\eqref{eq:vis_red} results in  
\begin{equation}
\label{eq:lincal}
d_{pq} =  e^{\eta_p - i \varphi_p} e^{\widetilde{\eta}_{\phi_{pq}}- i \widetilde{\varphi}_{\phi_{pq}}} e^{\eta_q + i \varphi_q} + n_{pq}.
\end{equation}

A possible approach one can use to solve the unknowns in Eq.~\eqref{eq:lincal} is to write down the Taylor expansion of the first term of the right hand side of Eq.~\eqref{eq:lincal} around some 
initial fiducial guess of $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$, which we denote with 
$\eta_p^0,\eta_q^0,\widetilde{\eta}_{\phi_{pq}}^0,\varphi_p^0,\varphi_q^0$ and $\widetilde{\varphi}_{\phi_{pq}}^0$, and then to solve the perturbations from this 
initial guess that minimize the difference between the right and left hand side of Eq.~\eqref{eq:lincal}. Once the perturbation values 
have been computed it is trivial to obtain an estimate of $g_i$, $g_j$ and $y_{\phi_{ij}}$.

If we Taylor expand the first term on the right hand side of Eq.~\eqref{eq:lincal} around a fiducial initial guess we obtain
\begin{equation}
\label{eq:taylor_expansion}
d_{pq} = v_{pq}^0[1+\Delta \eta_p + \Delta \eta_q + i \varphi_p - i \Delta \varphi_q + \Delta \widetilde{\eta}_{\phi_{pq}} + i\Delta \widetilde{\eta}_{\phi_{pq}}] + n_{pq}, 
\end{equation}
where
\begin{equation}
v_{pq}^0 = e^{\eta_p^0 - i \varphi_p^0} e^{\widetilde{\eta}_{\phi_{pq}}^0 - i \widetilde{\varphi}_{\phi_{pq}}^0} e^{\eta_q^0 + i \varphi_q^0}, 
\end{equation}
and $\eta_p^0,\eta_q^0,\widetilde{\eta}_{\phi_{pq}}^0,\varphi_p^0,\varphi_q^0$ and $\widetilde{\varphi}_{\phi_{pq}}^0$ respectively denote the initial guess for $\eta_p,\eta_q,\widetilde{\eta}_{\phi_{pq}},\varphi_p,\varphi_q$ and $\widetilde{\varphi}_{\phi_{pq}}$.
Eq.~\eqref{eq:taylor_expansion} can be used to construct the following linear system
\begin{equation}
\breve{\br} = \bJ\Delta\widehat{\bz}, 
\end{equation}
where 
\begin{equation}
\left [ \breve{\br} \right ]_{\alpha_{pq}} = d_{pq}-v_{pq}^0, 
\end{equation}
\begin{equation}
\label{eq:jac_lincal}
\bJ = \begin{bmatrix}
      \bN & \bM\\
      \conj{\bN} & \conj{\bM}
      \end{bmatrix}
\end{equation}
and
\begin{equation}
\Delta\widehat{\bz} = 
\begin{bmatrix}
\Delta \bmath{\eta} \\
\Delta \bmath{\varphi} \\
\Delta \widetilde{\bmath{\eta}} \\
\Delta \widetilde{\bmath{\varphi}},
\end{bmatrix}
\end{equation}
with
\begin{align}
 \Delta \bmath{\eta} &= [\Delta \eta_1,\Delta \eta_2,\cdots \Delta \eta_N]^T\nonumber\\
 \Delta \bmath{\varphi} &= [\Delta \varphi_1,\Delta \varphi_2,\cdots \Delta \varphi_N]^T\nonumber\\
 \Delta \widetilde{\bmath{\eta}} &= [\Delta \widetilde{\eta_1},\Delta \widetilde{\eta_2},\cdots \Delta \widetilde{\eta_N}]^T\nonumber\\
 \Delta \widetilde{\bmath{\varphi}} &= [\Delta \widetilde{\varphi_1},\Delta \widetilde{\varphi_2},\cdots \Delta \widetilde{\varphi_N}]^T.
\end{align}

Furthermore, 
\begin{equation}
\bN = \begin{bmatrix}
      \bN_1 & \bN_2 
      \end{bmatrix},
\end{equation}
with 
\begin{align}
[\bN_1]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \eta_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&= (\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq}^0,
\end{align}
and
\begin{align}
 [\bN_2]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \varphi_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
 &= (-1)^{\delta_{q}^{j}}i(\delta_{p}^{j}\vee\delta_{q}^{j}) v_{pq}^0. 
\end{align}

Moreover,
\begin{equation}
\bM = \begin{bmatrix}
      \bM_1 & \bM_2 
      \end{bmatrix},
\end{equation}
with
\begin{align}
[\bM_1]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \widetilde{\eta}_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&=  \delta_{\phi_{pq}}^{j} v_{pq}^0,
\end{align}
and
\begin{align}
[\bM_2]_{\alpha_{pq},j} &= \frac{\partial v_{pq}}{\partial \widetilde{\varphi}_j} {\bigg |}_{\widehat{\bz}=\widehat{\bz}^0}\\
&= i\delta_{\phi_{pq}}^{j} v_{pq}^0,
\end{align}

STILL NEEDS LOTS OF WORK.

@@

% fiducial initial guess 
% 
% The following partial derivatives are now easily computed
% 
% \begin{eqnarray}
% \frac{c_{ij}}{\partial \eta_p} &=& y_{i-j} e^{\eta_p - i \varphi_p} e^{\eta_q - i \varphi_q}\\ 
% \frac{c_{ij}}{\partial \varphi_p} &=&  -i y_{i-j} e^{\eta_p - i \varphi_p} e^{\eta_q - i \varphi_q}\\
% \frac{c_{ij}}{\partial \eta_q} &=& y_{i-j} e^{\eta_p - i \varphi_p} e^{\eta_q - i \varphi_q}\\ 
% \frac{c_{ij}}{\partial \varphi_q} &=&  i y_{i-j} e^{\eta_p - i \varphi_p} e^{\eta_q - i \varphi_q}\\
% \frac{y_{i-j}}{\partial \varphi_q} &=&  e^{\eta_p - i \varphi_p} e^{\eta_q - i \varphi_q}
% \end{eqnarray}
% 
% 
% The Wirtinger derivative is used in the last equation.
% 
% \begin{eqnarray}
% c_{ij} &\approx& c_{ij}^0 + \Delta \eta_p(y_{i-j}^0 e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0}) + \Delta \eta_q(y_{i-j}^0 e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0})\\
% && -i\Delta\varphi_p (y_{i-j}^0e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0}) +i\Delta\varphi_q (y_{i-j}^0e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0})\\
% && y_{i-j}^1(y_{i-j}^0e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0})\\
% &\approx&  c_{ij}^0 + e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_p+ \Delta \eta_q - i\Delta\varphi_p + i\Delta\varphi_p))
% \end{eqnarray}
% 
% \begin{equation}
% \label{eq:residual}
% r_{ij} = \delta_{ij} = c_{ij}-c_{ij}^0 = e^{\eta_p^0 - i \varphi_p^0} e^{\eta_q^0 - i \varphi_q^0}(y_{i-j}^1 + y_{i-j}^0( \Delta \eta_p+ \Delta \eta_q - i\Delta\varphi_p + i\Delta\varphi_p)) 
% \end{equation}
% 
% Eq.~\ref{eq:residual} allows us to construct the following linear system:
% 
% \begin{equation}
% \boldsymbol{J}[\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = \boldsymbol{r}, 
% \end{equation}
% 
% where $\boldsymbol{J}$ is equal to 
% \begin{equation}
% \boldsymbol{J} = \bigg [\overbrace{\frac{c_{pq}}{\partial \eta_p}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial \varphi_p}}^{i= 1\cdots N},~\overbrace{\frac{c_{pq}}{\partial y_{t}}}^{t=1\cdots r_s} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q) 
% \end{equation}
% or
% \begin{equation}
% \boldsymbol{J} = \bigg [\frac{c_{pq}}{\partial \boldsymbol{\eta}},~\frac{c_{pq}}{\partial \boldsymbol{\varphi}},~\frac{c_{pq}}{\partial \boldsymbol{y}} \bigg ] \bigg \} [pq] = 1\cdots N_{\textrm{b}} (p<q). 
% \end{equation}
% 
% The last column is again a Wirtinger derivative.
% 
% Which means we can obtain the least-squares estimate as follows:
% 
% \begin{equation}
% [\boldsymbol{\Delta \eta},\boldsymbol{\Delta \varphi},\boldsymbol{\Delta y}]^T = [\boldsymbol{J}^H\boldsymbol{J}]^{-1}\boldsymbol{J}^H\boldsymbol{r}.
% \end{equation}
